### 2019-02-25 conclusion.tex
mz - pass after 30 execution time

We present the design, implementation, and cost optimization for Seneca.
The optimizer automatically optimizes function memory use to reduce the cost
of AWS Lambda use.  Our empirical evaluation using
multiple applications for regression and classification (using
the models for prediction and not explanatory value), shows that Seneca is able to quickly
identify the best performing model for the applications and datasets that we consider.  
We also show that Seneca memory optimization reduces the cost of using
Seneca by 10-30\% for the applications studied.

>>>>

We present the design, implementation, and cost optimization for Seneca.
The optimizer automatically optimizes function memory use to reduce the cost
of AWS Lambda use.  Our empirical evaluation using
multiple applications for regression and classification (using
the models for prediction and not explanatory value), shows that Seneca is able to quickly
identify the best performing hyperparameter setting for the applications and datasets that we consider.  
We also show that Seneca memory optimization reduces the cost of using
Seneca by 10-30\% for the applications studied.

### 2019-02-25 results.tex
mz - pass after 30 execution time

\begin{table}[t]
\centering
%\scriptsize
%\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|} \hline
\textbf{Application}& \textbf{Description}\\
\hline
Prophet& Time series decomposition and prediction\\ 
\hline
Multi-Regression& Multiple linear regression/prediction of time series\\
\hline
XGBoost& Regression and classification by gradient boosting\\
\hline
SVC & Classification based on support vector machine\\
\hline
NN& Classification by layered artificial neural network\\
\hline
\end{tabular}
%}
\caption{Machine learning applications used as benchmarks
to evaluate Seneca. 
%paper submission is blind (so such references must be omitted so as not to reveal our identities):
%Code base is available at project repository~\cite{ref:seneca}.
\label{tab:bmarks}}
\vspace{-0.2in}
\end{table}

In this section,
we evaluate Seneca in terms of performance, monetary cost, 
and hyperparameter tuning time (latency), 
for different machine learning applications.
We first overview these applications and our empirical methodology. 
We then present our experimental results.

\begin{table}[t]
\centering
\scriptsize
%\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|l|} 
\hline
\textbf{Hyperparameter}& \textbf{Default} & \textbf{Tuning options}\\
\hline
grow & linear & [linear, logistic] \\
\hline
changepoint prior scale & 0.05 & [0.05, 0.5] \\
\hline
holidays prior scale & 10 & [1, 5, 10] \\
\hline
seasonality prior scale & 0.5 & [0.1, 0.5] \\
\hline
fourier order & 10 & [5, 10, 15, 20] \\
\hline
seasonality mode & additive & [additive, multiplicative] \\
\hline
interval width & 0.8 & [0.5, 0.8] \\
\hline
\end{tabular}
%}
\caption{The hyperparameters that Seneca considers for Prophet. 
The default value and tuning options are listed. 
\label{tab:prophet_para}}
%\vspace{-0.2in}
\end{table}

\begin{table}[t]
\centering
\scriptsize
\input{hparams-xgboost-tab}
\caption{The hyperparameters that Seneca considers for XGBoost. 
The default value and tuning options are listed. 
\label{tab:xgboost_para}}
%\vspace{-0.2in}
\end{table}

\begin{table}[t]
\centering
\scriptsize
\input{hparams-svc-tab}
\caption{The hyperparameters that Seneca considers for SVC. 
The default value and tuning options are listed. 
\label{tab:svc_para}}
%\vspace{-0.2in}
\end{table}

\begin{table}[t]
\centering
\scriptsize
\input{hparams-nn-tab}
\caption{The hyperparameters that Seneca considers for NN.
The default value and tuning options are listed. 
\label{tab:nn_para}}
\vspace{-0.2in}
\end{table}

@@

In the results that follow, we evaluate \textit{default} parameterizations (that come with 
the application or that are defined by the application developer) for each application.  
The default parameters and tuning options for Prophet are listed in the table~\ref{tab:prophet_para}. For every cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and n is the number of data points. Then the application returns the average MSE of all cross validation. Based on the model trained by default parameter setting, this average MSE metric is 0.284.

@@

These applications compute classification accuracy score
as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
prediction class, $Y_i$ is the true class, $n$ is the number of samples, and 1(x)
is the indicator function. XGBoost also computes MSE for its regression task
on the same datasets. The dataset has been filtered to remove correlated
features (those with an absolute value of the Pearson correlation coefficient
greater than 0.8). The dataset has also been balanced by down-sampling one
target whose number greatly exceeds other ones. The resulting dataset contains
33926 rows (individual fruit) distributed evenly to 5 targets and each row has
18 features.

@@

To evaluate Seneca, we measure tuning performance, application execution time,
and monetary cost.  For tuning performance, we use mean squared error (MSE)
for regression tasks and percentage accuracy for classification tasks (i.e. we score
model prediction accuracy and not explanatory power).  Because we use the same 
total number of hyperparameters for each model, the penalty function in terms of 
Bayesian Information Criteria, is the same. Thus, we can compare models using
this score.

@@

%We also experiment with different memory configurations for Seneca functions
%in AWS Lambda.  
We also investigate Seneca's automatic memory optimization capabilities.  To
do so we compare the execution performance and cost of the benchmarks using
the maximum allocatable memory size to the performance and cost when run with
Seneca's automatically determined memory size.  Note that this comparison
assume that the memory size used by each benchmark does not depend on
hyperparameter settings.  We have verified that this assumption holds for the
benchmarks and datasets we consider and plan to consider applications for
which hyperparameter settings require different maximum amounts of memory as
part of future work.

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
& Prophet & Multi-Regression & XGBoost\\
\hline
\# of Combinations & 384 & 255 & 768\\
\hline
\hline
Default MSE & 0.284 & 11.446 & 0.119 \\
\hline
Worst MSE & 1.266 & 43.752 & 8.98 \\
\hline
Best MSE (Seneca) & 0.220 & 9.621 & 0.044 \\
\hline
%percent difference between default and best 26.07%, 15.94%, 67.30%
%percent difference between worst and best 82.63%, 78.01%, 95.52%
%\begin{figure}[t] \centering 
%\includegraphics[scale=0.4]{mse}
\end{tabular}
\caption{Combination count and MSE for the default, best (Seneca's recommendation), and worst hyperparameter configurations for the three regression applications. 
For the MSE  values (rows 3-5), lower is better.
\label{tab:mse}}
\vspace{-0.2in}
\end{table}

@@

%Note that Seneca's recommendation is the best performing configuration.
Compared to the default hyperparameter settings,
Seneca reduces MSE by 26\%, 16\%, and 63\%, for Prophet, Multi-Regression, and XGBoost,
respectively, for the datasets and training methodologies that we consider.
Verses the worst case, Seneca reduces MSE by 83\%, 78\%, and 99\%, respectively.

@@

%%%%%%%%%%%%%%%%%%%%% classification apps - tuning performance
%%%%%%%%%%%%%%%%%%%%%%%%%%
We next empirically evaluate the tuning performance of Seneca for the three
classification applications: XGBoost (classification), SVC, and NN.
Table~\ref{tab:accuracy} presents the accuracy percentage (higher is
better) reported by each application (3 rightmost columns) for the default,
worst, and best hyperparameter tuning configurations reported by Seneca.
using an 80/20 (train/test) percent split,
Seneca increases accuracy by 3.43\%, 62.52\%, and 0.53\%, for XGBoost
(classification), SVC, and NN applications, respectively.  Compared to
the worst case, Seneca improves accuracy by 99.13\%, 75.75\%, and 65.57\%,
respectively.

\begin{table}
\centering
\begin{tabular}{|l|c|c|c|}
\hline
\textbf{80\%-20\%} & XGBoost & SVC & NN\\
\hline
\hline
Default Accuracy & 95.70\% & 21.77\% & 84.23\%\\
\hline
Worst Accuracy&0.00\%&7.53\% & 19.19\%\\
\hline
Best Accuracy (Seneca) &99.13\% & 83.29\% & 84.76\%\\
\hline
%\hline
%\hline
%\textbf{20\%-80\%} & XGBoost & SVC & NN\\
%\hline
%Default Accuracy & 95.07\% & 21.31\% & 55.44\%\\
%\hline
%Worst Accuracy&0.00\% & 9.42\% & 19.55\%\\
%\hline
%Best Accuracy (Seneca) & 98.68\% & 43.61\% & 60.89\%\\
%\hline
%\hline
%\textbf{0.1\%-99.9\%} & XGBoost & SVC & NN\\
%\hline
%Default Accuracy & 86.37\% & 20.02\% & 20.00\%\\
%\hline
%Worst Accuracy & 0.00\% & 19.99\% & 19.79\%\\
%\hline
%Best Accuracy (Seneca) & 89.14\% & 55.79\% & 29.99\%\\
%\hline

%percent difference between default and best 83.65%, 83.84%, 79.83%
%percent difference between worst and best 86.07%, 85.73%, 84.63%
%\begin{figure}[t] \centering 
%\includegraphics[scale=0.38]{accuracy}
\end{tabular}
\caption{The Accuracy reported for the 
default, best (Seneca's recommendation), and worst hyperparameter configurations for 
the three classification applications using 80\% of the data to train and 20\%
of the data as a test set. 
%under three train/test split scenarios.  
For the accuracy values in the table, higher is better.
\label{tab:accuracy}}
\vspace{-0.2in}
%\end{figure}
\end{table}

The 80-20 case represents the typical usage of these classification
applications.  Often, when evaluating the accuracy of a specific classifier,
the user uses the 80-20 split ``rule'' when measuring accuracy.  In this case,
Seneca's improvement over the default parameterizations varies from less than
1\% for the Neural Network (NN) application (column 4), to 61.5\% for SVC
(best versus default in column 3).

@@

Figure~\ref{fig:box_plot_accuracy} presents the accuracy (higher is better) 
for the entire hyperparameter search space for each classification
application.  The central rectangle covers from first quartile to third quartile (Q3 - Q1) and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}. The red notch indicates the accuracy metric from the model trained by default settings and colored diamonds are outliers beyond whiskers.
For both types of applications (regression and classification), Seneca significantly
improves tuning performance over the default and worst case configurations for 
XGBoost and SVC while generating only a small improvement over the
default for NN.

@@

We next analyze the monetary costs incurred by Seneca.  To do so, we
use Seneca to find the hyperparameterization that optimizes application output
quality (lowest MSE for regression, highest accuracy for classification).
For each hyperparameterization that Seneca evaluates, it incurs a
cost. Furthermore, the amount of memory used by Seneca during memory
tuning also influences overall cost.

Thus, instead of trying out all possible settings,  we compare two
Seneca execution configurations.  In the first 
we configure each lambda function to
use the maximum amount of memory allowed by AWS Lambda (3008 MB) for all
executions.
Second, we
employ Seneca's memory optimization which automatically detects and configures
the amount of memory needed by each function.  This optimization requires
Seneca to ``probe'' to determine the best memory size to use.  The
cost of these probes
(denoted ``Optimizer Cost'') must be taken into account as well.
%Because memory impacts both
%cost and execution time (total latency of Seneca hyperparameter tuning), we
%present empirically evaluate both in this subsection.  
Note that XGBoost's performance profile is identical when used for regression
or classification so we include its measurements only once in the following
analysis.
%For each, we only
%include XGBoost once since its performance profile is the same regardless of
%whether we are using regression or classification.

\begin{table}
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline
& Prophet & MR & XGBoost & SVC & NN\\
\hline
\hline
Exec time (minutes)& 24.96 & 4.18 & 17.48 & 0.91 & 2.49 \\
\hline
Seneca Cost (\$) & 0.722 & 0.121 & 0.5 & 0.023 & 0.072 \\
\hline
\end{tabular}
\caption{Monetary cost of using Seneca for hyperparameter tuning when configured to use the maximum amount of memory (3008 MB) possible for each function invocation. 
\label{tab:cost_max_memory}}
%\vspace{-0.2in}
\end{table}

\begin{table}
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline
& Prophet & MR & XGBoost & SVC & NN\\
\hline
\hline
Exec time (minutes)& 38.7 & 8.72 & 29.07 & 0.91 & 3.17 \\
\hline
Optimizer Cost (\$) &0.033 & 0.014 & 0.003 & 0.010 & 0.008 \\
\hline
Seneca Cost (\$) &0.62 & 0.086 & 0.354 & 0.007 & 0.056 \\
\hline
Total Cost (\$) &0.653 & 0.1 & 0.357 & 0.016 & 0.064 \\
\hline
\hline
Savings (\$) & 0.07 & \$0.02 & 0.15 & 0.007 & 0.008\\
\hline
Savings (\%) & 10\% & 17\% & 30\% & 30\% & 11\%\\
\hline
\end{tabular}
\caption{Seneca Memory Optimization:  The  monetary  cost  of using Seneca for hyperparameter tuning when the amount of memory  used  for  each  function  invocation  is  automatically inferred and set by Seneca.
\label{tab:cost_optimized}}
\vspace{-0.2in}
\end{table}

Tables~\ref{tab:cost_max_memory} and~\ref{tab:cost_optimized} show the results with and without 
the Seneca memory optimization, respectively. In both tables, the five columns identify the 
benchmark applications and the first row is the total execution time in minutes for 
Seneca's hyperparameter tuning for the corresponding application.  
In Table~\ref{tab:cost_max_memory}, the second row is total cost of tuning when Seneca's 
lambda functions are configured to use the maximum amount of memory (3008 MB). 
Table~\ref{tab:cost_optimized} shows the cost of the memory optimizer in the
second row, Seneca's cost using the optimization in the third row, and total cost on fourth row.
Finally, in the fifth and six rows of Table~\ref{tab:cost_optimized} we show the
savings that memory optimization introduces over using the maximum memory in
dollar cost and as a percentage respectively.

These tables illustrate two important cost features of Seneca.  First, using
AWS Lambda, full hyperparameter space exploration is not expensive in 
\textit{absolute} dollar cost terms.  Even using the maximum memory available
for almost 25 minutes of execution time (cf Prophet in Table~\ref{tab:cost_max_memory}), the
total dollar cost is approximately 73 cents.  Secondly, Seneca's memory
optimizations produce a significant percentage savings which, over repeated
executions, is important.

Note also that Seneca's memory/cost optimization
introduces at an execution time penalty (relative to the maximum memory
execution) for some of the applications.  That is, the
execution times for all applications except SVC increase when Seneca chooses
a memory size.  Thus while Seneca is finding the best application output
quality and optimizing the cost of producing that output, it is doing so at
the expense of execution performance (time to solution). Such a penalty
is expected due to the proportional CPU power to allocated
memory. However, the Seneca optimizer is able to find the optimal
memory configuration to minimize that  penalty. In the case of SVC, Seneca saves 30\% compared to max memory execution (\$0.016 vs \$0.023) but has the same execution time (0.91 minutes).
% The source of this execution performance penalty is not clear.  We hypothesize
% that when requesting a large memory for AWS Lambda, Amazon chooses a machine
% that also has fast processors so the Lambda functions execute more quickly.
% If this supposition is true, then the AWS Lambda pricing model correctly
% weights the cost of additional memory (in light of the reduced execution time)
% because the large-memory executions are still more expensive.
%However regardless of the cause, 
Even in the worst case of CPU-bound application, the Seneca memory optimizer still provides a way to trade off time to solution for cost when the highest possible application output quality is desired.
% \textcolor{blue}{AWS announces the proportional CPU power to memory which is the source of penalty}
% \textcolor{blue}{See my notes to fix the tables in the caption of these figures.}

>>>>

\begin{table}[t]
\centering
\input{tables/application-tab}
\caption{Machine learning applications used as benchmarks
to evaluate Seneca. 
%paper submission is blind (so such references must be omitted so as not to reveal our identities):
%Code base is available at project repository~\cite{ref:seneca}.
\label{tab:bmarks}}
\vspace{-0.2in}
\end{table}

In this section,
we evaluate Seneca in terms of performance, monetary cost, 
and hyperparameter tuning execution time, 
for different machine learning applications.
We first overview these applications and our empirical methodology. 
We then present our experimental results.

\begin{table}[t]
\centering
\input{tables/hparams-prophet-tab}
\caption{The hyperparameters that Seneca considers for Prophet. 
The default value and tuning options are listed. 
\label{tab:prophet_para}}
%\vspace{-0.2in}
\end{table}

\begin{table}[t]
\centering
\scriptsize
\input{tables/hparams-xgboost-tab}
\caption{The hyperparameters that Seneca considers for XGBoost. 
The default value and tuning options are listed. 
\label{tab:xgboost_para}}
%\vspace{-0.2in}
\end{table}

\begin{table}[t]
\centering
\scriptsize
\input{tables/hparams-svc-tab}
\caption{The hyperparameters that Seneca considers for SVC. 
The default value and tuning options are listed. 
\label{tab:svc_para}}
%\vspace{-0.2in}
\end{table}

\begin{table}[t]
\centering
\scriptsize
\input{tables/hparams-nn-tab}
\caption{The hyperparameters that Seneca considers for NN.
The default value and tuning options are listed. 
\label{tab:nn_para}}
\vspace{-0.2in}
\end{table}

@@

In the results that follow, we evaluate \textit{default} parameterizations (that come with 
the application or that are defined by the application developer) for each application.  
The default parameters and tuning options for Prophet are listed in the Table~\ref{tab:prophet_para}. For every cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and n is the number of data points. Then the application returns the average MSE of all cross validation. Based on the model trained by default parameter setting, this average MSE metric is 0.284.

@@

These applications compute classification accuracy score
as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
prediction class, $Y_i$ is the true class, $n$ is the number of samples, and 1(x)
is the indicator function. XGBoost also computes MSE for its regression task
on the same datasets. The dataset has been filtered to remove correlated
features (those with an absolute value of the Pearson correlation coefficient
greater than 0.8). The dataset has also been balanced by down-sampling and the resultant dataset contains
33926 rows (individual fruit) distributed evenly to 5 targets and each row has
18 features.

@@

To evaluate Seneca, we measure tuning performance, application execution time and memory use,
and monetary cost.  For tuning performance, we use mean squared error (MSE)
for regression tasks and percentage accuracy for classification tasks (i.e. we score
model prediction accuracy and not explanatory power).  Because we use the same 
total number of hyperparameters for each model, the penalty function in terms of 
Bayesian Information Criteria, is the same. Thus, we can compare models using
this score.

@@

%We also experiment with different memory configurations for Seneca functions
%in AWS Lambda.  
We also investigate Seneca's automatic memory optimization capabilities.  To
do so we compare the execution performance and cost of the benchmarks using
the maximum allocatable memory size to the performance and cost when run with
Seneca's automatically determined memory size. Though memory size used reported by AWS CloudWatch fluctuates throughout the tuning process, we have verified the optimized allocated memory allows all hyperparameter settings run successfully.

% Note that this comparison assumes that the memory size used by each benchmark does not depend on hyperparameter settings. We have verified that this assumption holds for the benchmarks and datasets we consider and plan to consider applications for which hyperparameter settings require different maximum amounts of memory as part of future work.

@@

\begin{table}
\centering
\input{tables/mse-tab}
\caption{Combination count and MSE for the default, best (Seneca's recommendation), and worst hyperparameter configurations for the three regression applications. 
For the MSE  values (rows 3-5), lower is better.
\label{tab:mse}}
%\vspace{-0.2in}
\end{table}

@@

%Note that Seneca's recommendation is the best performing configuration.
Compared to the default hyperparameter settings,
Seneca reduces MSE by 22.56\%, 15.94\%, and 62.69\%, for Prophet, Multi-Regression, and XGBoost, respectively, for the datasets and training methodologies that we consider.
Verses the worst case, Seneca reduces MSE by 82.62\%, 78.01\%, and 99.51\%, respectively.

@@

%%%%%%%%%%%%%%%%%%%%% classification apps - tuning performance
%%%%%%%%%%%%%%%%%%%%%%%%%%
We next empirically evaluate the tuning performance of Seneca for the three
classification applications: XGBoost (classification), SVC, and NN.
Table~\ref{tab:accuracy} presents the accuracy percentage (higher is
better) reported by each application (3 rightmost columns) for the default,
worst, and best hyperparameter tuning configurations reported by Seneca.
using an 80/20 (train/test) percent split,
Seneca increases accuracy by 2.46\%, 19.04\%, and 3.79\%, for XGBoost
(classification), SVC, and NN applications, respectively.  Compared to
the worst case, Seneca improves accuracy by 98.11\%, 26.74\%, and 63.92\%,
respectively.

\begin{table}
\centering
\input{tables/accu-tab}
\caption{The Accuracy reported for the 
default, best (Seneca's recommendation), and worst hyperparameter configurations for 
the three classification applications using 80\% of the data to train and 20\%
of the data as a test set. 
%under three train/test split scenarios.  
For the accuracy values in the table, higher is better.
\label{tab:accuracy}}
\vspace{-0.2in}
%\end{figure}
\end{table}

The 80-20 case represents the typical usage of these classification
applications. Often, when evaluating the accuracy of a specific classifier,
the user uses the 80-20 split ``rule'' when measuring accuracy. In this case,
Seneca's improvement over the default parameterizations varies from 2.46\% for XGBoost application (column 2), to 19.04\% for SVC
(column 3).

@@

Figure~\ref{fig:box_plot_accuracy} presents the accuracy (higher is better) 
for the entire hyperparameter search space for each classification
application.  The central rectangle covers from first quartile to third quartile (Q3 - Q1) and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}. The red notch indicates the accuracy metric from the model trained by default settings and colored diamonds are outliers beyond whiskers.
For both types of applications (regression and classification), Seneca significantly
improves tuning performance over the default and worst case configurations for SVC while generating a relatively small improvement over the default for XGBoost and Neural Network. This is because powerful classifiers, like XGBoost and Neural Network, can achieve fairly good accuracy by default setting, whereas weaker classifier, like SVC, requires more tuning to reach high accuracy.

\begin{table}[t]
\centering
\scriptsize
\input{tables/exec-time-memory-tab}
\caption{The mean (stdev) values of execution time and memory use, and best accuracy across 30 executions of three classification benchmarks running against two random states. It verifies data split does not have major impact to execution metrics and scores.
\label{tab:exec_memory}}
%\vspace{-0.2in}
\end{table}

In order to investigate the potential impact from data split, we split the data for three classification applications by two random states, run Seneca 30 times and obtain execution time, memory use and best accuracy from AWS CloudWatch logs. As showed in Table~\ref{tab:exec_memory}, different data split has no major impact to these three values. It does not only mean the execution time and monetary cost are consistent given various data splits, but also indicates users do not have to run Seneca repetitively in the inference phase when new data are generated.

% \begin{table}
% \centering
% \input{tables/speedup-tab}
% \caption{The execution time of tuning in seconds by using Seneca and EC2 instance (Serial) and respective speedup. 
% \label{tab:accuracy}}
% \vspace{-0.2in}
% \end{table}

Finally in this section, we contrast the execution time of Seneca with serial hyperparameter tuning process on EC2 instance across five applications. Since library compilation issue, we use t2.medium on Prophet and t2.micro on other 4 applications. As a result, Seneca achieves at least 4x speedup for IO-bound application (SVC) and 21x speedup for CPU-bound application (XGBoost). It confirms Seneca can execute tuning within a more reasonable period of time, comparing to executing serially on EC2 instance.

@@

% To do so, we use Seneca to find the hyperparameterization that optimizes application output
% quality (lowest MSE for regression, highest accuracy for classification).
% For each hyperparameterization that Seneca evaluates, it incurs a
% cost. Furthermore, the amount of memory used by Seneca during memory
% tuning also influences overall cost.

We next analyze the monetary costs incurred by Seneca. Instead of trying out all possible settings,  we compare two
Seneca execution configurations.  In the first 
we configure each lambda function to
use the maximum amount of memory allowed by AWS Lambda (3008 MB) for all
executions.
Second, we employ Seneca's memory optimization which automatically detects and configures
the amount of memory needed by each function.  This optimization requires
Seneca to ``probe'' to determine the best memory size to use.  The
cost of these probes
(denoted ``Optimizer Cost'') must be taken into account as well.
%Because memory impacts both
%cost and execution time (total latency of Seneca hyperparameter tuning), we
%present empirically evaluate both in this subsection.  
Note that XGBoost's performance profile is identical when used for regression
or classification so we include its measurements only once in the following
analysis.
%For each, we only
%include XGBoost once since its performance profile is the same regardless of
%whether we are using regression or classification.

Tables~\ref{tab:cost_optimized} shows the results with and without 
the Seneca memory optimization, respectively. The five columns identify the benchmark applications and the first row is the total execution time in minutes and the second row is total cost of tuning when Seneca's lambda functions are configured to use the maximum amount of memory (3008 MB). For optmized memory configuration, fourth row shows the cost of the memory optimizer in the
second row, Seneca's cost using the optimization in the fifth row, and total cost on sixth row.
Finally, in the seventh and eighth rows of Table~\ref{tab:cost_optimized} we show the
savings that memory optimization introduces over using the maximum memory in dollar cost and as a percentage respectively.

\begin{table}
\centering
\input{tables/seneca-mem-opt-tab.tex}
\caption{Seneca Memory Optimization: First two rows show the execution time and  monetary cost of using Seneca at max memory (3008 MB). Row 3-6 show the execution time and cost when the amount of memory used for each function invocation is automatically inferred and set by Seneca. Row 7-8 show savings by dollar and percentage.
\label{tab:cost_optimized}}
\vspace{-0.2in}
\end{table}

Table~\ref{tab:cost_optimized} illustrates two important cost features of Seneca.  First, using
AWS Lambda, full hyperparameter space exploration is not expensive in 
\textit{absolute} dollar cost terms.  Even using the maximum memory available
for almost 25 minutes of execution time (cf Prophet in Table~\ref{tab:cost_optimized}), the
total dollar cost is approximately 73 cents.  Secondly, Seneca's memory
optimizations produce a significant percentage savings which, over repeated
executions, is important.

Note also that Seneca's memory/cost optimization
introduces at an execution time penalty (relative to the maximum memory
execution) for some of the applications.  That is, the
execution times for all applications increase when Seneca chooses
a memory size.  Thus while Seneca is finding the best application output
quality and optimizing the cost of producing that output, it is doing so at
the expense of execution performance (time to solution). Such a penalty
is expected due to the proportional CPU power to allocated
memory. However, the Seneca optimizer is able to find the optimal
memory configuration to minimize that  penalty. In the case of SVC, Seneca saves 30\% compared to max memory execution (\$0.016 vs \$0.023) but has almost the same execution time (1.91 vs 1.95 minutes).
% The source of this execution performance penalty is not clear.  We hypothesize
% that when requesting a large memory for AWS Lambda, Amazon chooses a machine
% that also has fast processors so the Lambda functions execute more quickly.
% If this supposition is true, then the AWS Lambda pricing model correctly
% weights the cost of additional memory (in light of the reduced execution time)
% because the large-memory executions are still more expensive.
%However regardless of the cause, 
Even in the worst case of CPU-bound application, the Seneca memory optimizer still provides a way to trade off time to solution for cost when the highest possible application output quality is desired.

To corroborate the cost-effectiveness of Seneca, we analyzed the total cost of five benchmarks in 30 executions from last section. We observe the reported \textit{billed duration} and \textit{max memory used} oscillate that leads to different total cost across 30 executions and we assume it is because the pagination and memory sampling method used by different AWS Lambda host servers. However, even taking fluctuation into account, the highest cost of execution under optimized memory is still cheaper than the lowest cost of execution under maximum memory in all five benchmarks. We believe Seneca's optimizer is economical despite the locality of lambda container and application.

% \textcolor{blue}{AWS announces the proportional CPU power to memory which is the source of penalty}
% \textcolor{blue}{See my notes to fix the tables in the caption of these figures.}
